Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-07-04 paper.qmd
Update Figure 4

```{r}
# Code to draw illustration for notation
start_pt <- all_centroids_df |> 
  filter(hexID == 1)
d_rect <- tibble(x1min = 0, 
                 x1max = 1,
                 x2min = 0,
                 x2max = r2)
c_start <- tibble(s1 = 0.03, s2 = 0.05)
a1 <- tibble(x = all_centroids_df$c_x[21],
             xend = all_centroids_df$c_x[22],

@@

```{r}
#| label: fig-hex-param
#| fig-cap: "The components of the hexagon grid illustrating notation."
#| out-height: 30%
#| fig-width: 2.5
#| fig-height: 3.75
#| fig-pos: H

>>>>

```{r}
# Code to draw illustration for notation
start_pt <- all_centroids_df |> 
  filter(hexID == 1)
d_rect <- tibble(x1min = 0, 
                 x1max = 1,
                 x2min = 0,
                 x2max = r2)
#c_start <- tibble(s1 = 0.03, s2 = 0.05)
c_start <- tibble(s1 = 0.03, s2 = -0.05)

a1 <- tibble(x = all_centroids_df$c_x[4],
             xend = all_centroids_df$c_x[5],

@@

```{r}
#| label: fig-hex-param
#| fig-cap: "The components of the hexagon grid illustrating notation."
#| out-height: 30%
#| fig-width: 2.5
#| fig-height: 3.3
#| fig-pos: H
